---
title: "Biostat 607 Homework3"
output: html_notebook
---


```{r}
library(faraway)
data(nepali)
library(tidyverse)
library(dplyr) 
```

```{r}
nepali
```

(a) How many unique children (i.e., unique values of the id variable) are there in this
dataset? Create a new variable called num.id (a vector of length one) which is
equal to the number of unique ID's in this dataset.
There are 200 unique children in this dataset.
```{r}
id.freq = nepali$id %>% table() 
id.freq1 = as.data.frame(id.freq)
id.freq1
nepali$num.id = id.freq1$Freq
nepali
```
(b) Convert the id variable in nepali to a character variable.
```{r}
nepali$id = as.character(nepali$id) 
nepali$id %>% is.character()
```
(c) The first two digits of the id number represent the panchayat number. Add a
new variable called panchayat to the nepali data frame which is equal to the
first two digits of the id variable. The function substr will probably be useful
for this step.
```{r}
nepali$panchayat = substr(nepali$id,1,2)
nepali$panchayat
```
(d) How many unique panchayats are in this dataset?
There are three unique panchayats in this dataset.
```{r}
nepali$panchayat %>% unique() %>% table()
```
(e) The first five digits of the id represent the household identifier. Add a new called
house_id to the nepali data frame which is equal to the first five digits of the
id variable. The function substr will also be useful for this step.
```{r}
nepali$house_id = substr(nepali$id,1,5)
nepali$house_id
```
(f) Some of the observations on children are missing a weight (wt) value. How many
observations have a missing weight value?
There are 123 missing values for weight.
```{r}
nepali$wt %>% is.na() %>% table()
```
(g) Add a new variable to nepali called visit using the following code:
```{r}
nepali$visit <- rep(1:5, num.id)
```


```{r}
nepali$visit <- rep(1:5)
head(nepali, 10)
```
(h) Create a new data frame called nepali1 which only contains the observations
that have visit == 1.
```{r}
nepali1 = nepali %>% filter(visit==1)
nepali1
```
(i) Using nepali1, compute the mean child age (the age variable) in each panchayat.
```{r}
nepali1 %>%  group_by(panchayat) %>% summarise(mean.age = mean(age))
```
(j) Also, using nepali1, compute the correlation (using the R function cor) between
mother's age (mage) and age of child (age) in each panchayat.
```{r}
nepali1 %>% group_by(panchayat) %>% summarize(COR=cor(mage,age))
```


